Response to reviewers

### 2025-07-04 src/docs_paper-jtb/revisions.Rmd
Refer to figures by number and add NUTS rerun details

Some HIV surveys provide bio-marker data on whether or not the infection was recent.
The equation in the manuscript links the probability of recent infection to HIV prevalence, HIV incidence, and properties of the recent infection assay.
This allows us to back-out estimates of the HIV incidence.
<!-- Is there something to add to the manuscript here? -->

@@

@@

Thank you for the suggestion.
We have adjusted the `alpha` value from 0.5 to 0.1 and added a caption to the figure explaining the possible overlap to make the figure clearer:

@@

We agree that there are too many colours here for this figure to be clear, and that the suggestion to split the figure across panels is a good one.
To do so, we have grouped the parameters by the model component (e.g. HIV prevalence), and used colour to represent the type of parameter (e.g. intercept).

>>>>

Some HIV surveys provide bio-marker data on whether or not the infection was recent.
Equation 7 links the probability of recent infection to HIV prevalence, HIV incidence, and properties of the recent infection assay.
This allows us to back-out estimates of the HIV incidence.
<!-- Is there something to add to the manuscript here? -->

@@

We agree that running more iterations of the NUTS sampler is a good idea, and could improve the minimum ESS and accuracy of any comparisons, especially distributional ones.
We have rerun the NUTS sampler using a HPC with the 18 chains (across 18 cores) with 120,000 iterations each.

@@

Thank you for the suggestion.
We have adjusted the `alpha` value from 0.5 to 0.1 and added a caption to the figure explaining the possible overlap to make Figure 5 clearer:

@@

We agree that there are too many colours here for this figure to be clear, and that the suggestion to split the figure across panels is a good one.
To do this, we have grouped the parameters by the model component (e.g. HIV prevalence), and used colour to represent the type of parameter (e.g. intercept).
The updated version of Figure 7 is shown below:
